---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# shiny_gliders

<!-- badges: start -->

<!-- badges: end -->

This tool started as a means to view full datasets for Slocum glider vehicle troubleshooting and performance analysis. After creating a UI and handful of standardized means of plotting full missions, we extended the same framework to view and explore real-time decimated datasets as they come in from gliders currently in the water. Requires [osgUtils](https://github.com/oceanscienceguru/osgUtils) R package to function.

Minimal sbdlist requirements for full features:

```         
c_wpt_lat              #at least once per surfacing interval
c_wpt_lon              #at least once per surfacing interval
m_present_time         #as frequent as possible
m_coulomb_amphr_total  #at least once per surfacing interval
m_gps_lat              #as frequently as possible (only writes with gps lock)
m_gps_lon              #as frequently as possible (only writes with gps lock)
m_leakdetect*          #as often as desired
```

Minimum tbdlist requirements:

```         
sci_m_present_time     #as frequent as possible
sci_water_conductivity #as often as desired
sci_water_temperature  #as often as desired
sci_water_pressure     #as often as desired
```

Able to process intermediate and full data \*bd and \*cd files after conversion into ASCII format using standard `dbd2asc` tool from Teledyne.

# Setup

The original deployment of this app was on an Intel NUC running [Shiny Server](https://posit.co/products/open-source/shiny-server/ "Link to Posit's Shiny Server page"). This machine is on the same network as the primary Slocum glider dockserver. A cron job (see gliderCopy.sh file for example) synchronizes the from-glider and archive folders from the primary server to the remote server for processing for the app using rsync. Each synchronization uses the default `dbd2asc` program for Linux from Teledyne to convert the binary glider data into ASCII format as a standard .ssv. The outputted .ssv files need to be arranged in a specific folder structure for the R conversion cron job to function as expected (see below). Each data type (flight/science) needs to end up in its respective folder (`/echos` is the top level in this example).

```         
-- echos
   |__gliders
      |__usf-bull
         |__flight
         |__science
```

Next, the R conversion script (gliderChron.R) requires a similar, separate folder structure (see below). Within each glider's folder, two .csv files are maintained and a .RData containing all of the objects used for live data display.

```         
-- echos
   |__processed-gliders
      |__usf-bull
```

This script reads a controlling file ("processGliders.txt") that contains a list of glider names and battery capacities that informs which glider data should be processed. Glider names can be commented out when not in use. Similarly, the "deployedGliders.txt" file controls which gliders are actively displayed on the dashboard and follows the same structure. In the example below, usf-bass is a G1 glider and does not have a coulomb amphr counter board, so capacity is marked as 000 and none of the amphr-specific calculations will be displayed. As well, usf-jaialai is commented out and will not be processed on the cron job.

```         
#usf-jaialai 550
usf-bass     000
usf-gansett  215
```

Additionally, one may store example goto_l\*.ma files on the server in a folder named "routes" under the top level directory. These can be used for quick checks or route planning using the routing module.

Similarly, a standard naming convention for full datasets is used to parse mission information. Example: M139_usf-bull.RData parses out the mission name/number "M139" and the glider name "usf-bull". The source data for the full data import function is a .ssv of the entire mission containing both flight and science data after it has been merged into a single .ssv.

# Example daily email

Generated using the batteryMarkdown.Rmd script in Documentation. A dedicated cron job runs this markdown script via batteryMarkdownGenerate.R for each glider listed under the controlling file called "processGliders.txt".

------------------------------------------------------------------------

```{r, echo=FALSE}
htmltools::includeHTML("./Documentation/batteryMarkdown.html")
```

------------------------------------------------------------------------

This is then saved as an html file and emailed out daily using a separate cron job to a given list of emails.
