---
author: "Earle"
date: "`r Sys.Date()`"
output: html_document
params:
  gliderName: "usf-bass"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
knit_engines$set(asis = function(options) {
  if (options$echo && options$eval) knit_child(text = options$code)
})
```

```{r, include=FALSE}
### battery publishing ###
library(tidyverse)
library(lubridate)
library(terra)
library(osgUtils)
  
#source("/srv/shiny-server/thebrewery/scripts/gliderGPS_to_dd.R")

#i <- "usf-gansett"
#load(paste0("/echos/", i, "/glider_live.RData"))

load(paste0("/echos/", params$gliderName, "/glider_live.RData"))

  if (ahrCap > 0){
    recoDays <- format(round(((ahrCap*.9)-ahrUsed)/ahr3day, 2), nsmall = 2) #calculate days til 10% abort level
  } else {
    recoDays <- format(round(battLeft), nsmall = 2)
  }

currTime <- max(gliderdf$m_present_time, na.rm = TRUE)
dayAgo <- interval(currTime, currTime + days(-1))
day3Ago <- interval(currTime, currTime + days(-3))


dailydf <- gliderdf %>%
  filter(m_present_time %within% dayAgo) %>%
      mutate(latt = format(m_gps_lat, nsmall = 4),
             longg = format(m_gps_lon, nsmall = 4)) %>% #coerce to character keeping zeroes out to 4 decimals
      mutate(lat = gliderGPS_to_dd(latt),
             long = gliderGPS_to_dd(longg))

rolldf <- dailydf %>%
  select(c(m_present_time, m_roll, osg_i_depth)) %>%
  filter(!is.na(m_roll)) %>%
  filter(osg_i_depth > 2) %>%
  mutate(lagRoll = lag(m_roll)) %>%
  mutate(deltaRoll = (m_roll - lagRoll)*180/pi) %>%
  mutate(deltaRoll = abs(deltaRoll)) %>%
  filter(deltaRoll == max(deltaRoll, na.rm = TRUE)) %>%
  tail(1)

maxRoll <- as.logical(max(rolldf$deltaRoll > 10))

    #get commanded wpt, might not have ^F within 24hrs
    cwpt <- gliderdf %>%
      select(m_present_time, c_wpt_lat, c_wpt_lon) %>%
      filter(!is.na(c_wpt_lat)) %>%
      select(!c(m_present_time)) %>%
      format(., nsmall = 4) %>% #coerce to character keeping zeroes out to 4 decimals
      tail(1)  %>% 
      mutate(lat = gliderGPS_to_dd(c_wpt_lat),
             long = gliderGPS_to_dd(c_wpt_lon)) %>%
      select(c(long, lat))

pos <- dailydf %>%
  select(c(long, lat)) %>%
  filter(!is.na(lat))

posTime <- dailydf %>%
  select(m_present_time, lat) %>%
  filter(!is.na(lat)) %>%
  tail(1)
  
dist <- sum(distance(as.matrix(pos), lonlat = TRUE, sequential = TRUE))
toGo <- sum(distance(as.matrix(tail(pos, 1)), as.matrix(cwpt), lonlat = TRUE))

daysDep <- (min(gliderdf$m_present_time) %--% max(gliderdf$m_present_time))/days(1)

```

##### **Power Usage**

Days deployed: `r round(daysDep, 2)`

Battery voltage last 24hrs: `r round(mean(dailydf$m_battery, na.rm = TRUE), 2)`

Approximate time until 11V threshold: `r recoDays` days (calculated based on standard G1 voltage curve)

------------------------------------------------------------------------
```{asis, echo = maxRoll}
##### **Flight Anomalies**

There was a roll incident of `r round(rolldf$deltaRoll, 2)` degrees at `r round(rolldf$osg_i_depth, 2)` meters deep that occurred at `r rolldf$m_present_time`

------------------------------------------------------------------------
```

##### **Progress**

Distance covered in last 24hrs: `r round(dist/1000, 2)` km

As of `r posTime$m_present_time` UTC, `r params$gliderName` is `r round(toGo/1000, 2)` km from the next waypoint.

------------------------------------------------------------------------

This is the daily summary for `r params$gliderName`. For full data, see <http://earle.marine.usf.edu:3838/thebrewery/>.
